Reaching is Better When You Get What You Want: Realtime Feedback of Intended Reaching Trajectory Despite an Unstable Environment

### 2015-06-10 Paper2frontiers/frontiers.tex
update with jim

\section{Results}
As expected, the model was able to deduce an intended trajectory and all subjects were able to utilize this estimate of their intent to perform targeted reaching while experiencing turbulent forces (Figure 1). The following sections address the quality of this reaching.

\subsection*{Reaching Accuracy}
Even if subjects were capable of using IF to perform a reaching task, a poor estimate would have lead to poor performance. Indeed, the hand significantly outperformed our intent estimate when the force disturbance is not present in block 1 (Figure 2D). Model and sensor inaccuracies degrade performance and result in an error of approximately 5 millimetres. In the presence of a force disturbance in block 2, the hand loses its advantage as model and sensor inaccuracies are balanced by some degree of cancellation of the disturbance. In block 3 where visual feedback of the intent is given instead of hand, the intent significantly outperforms the hand. For this intent estimate to be useful, subjects should perform better when using feedback of the intent than when using feedback of the hand. Comparing the hand's performance in block 2 to the intent's performance in block 3, subjects performed significantly better using their estimated intent. Finally, no significant differences were present across the two experiments. Performance was relatively insensitive to this change in the stiffness model used to deduce the intent.

>>>>

\section{Results}
As expected, the model was able to deduce an intended trajectory and all subjects were able to use this estimate of their intent to perform targeted reaching while experiencing turbulent forces (Figure 1). The following sections address the quality of this reaching.

\subsection*{Reaching Accuracy}
The results do indeed show that performance using IF feedback exceeds that of truthful feedback of the hand. Even if subjects were capable of using IF to perform a reaching task, a poor estimate would have led to poor performance. Indeed, the hand significantly outperformed our intent estimate when the force disturbance is not present in block 1 (Figure 2D). Model and sensor inaccuracies degrade performance and result in an error of approximately 5 millimetres. In the presence of a force disturbance in block 2, the hand loses its advantage as model and sensor inaccuracies are balanced by some degree of cancellation of the disturbance. In block 3 where visual feedback of the intent is given instead of hand, the intent significantly outperforms the hand. For this intent estimate to be useful, subjects should perform better when using feedback of the intent than when using feedback of the hand. Comparing the hand's performance in block 2 to the intent's performance in block 3, subjects performed significantly better using their estimated intent. Finally, no significant differences were present across the two experiments. Performance was relatively insensitive to this change in the stiffness model used to deduce the intent.
